\textbf{ Interpretable Gaussian Processes for Stellar Variability\\ I: Static Surfaces }

### 2020-12-13 tex/gitlinks.tex
set randomizer seed for test, duh

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/5781bddaacfcc41fd945fb4973484b36d4d5e68b/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/5781bddaacfcc41fd945fb4973484b36d4d5e68b/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/5781bddaacfcc41fd945fb4973484b36d4d5e68b/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/1b565f496cf77b50c5eb4b5279cee8f687f36b27/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/1b565f496cf77b50c5eb4b5279cee8f687f36b27/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/1b565f496cf77b50c5eb4b5279cee8f687f36b27/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}

### 2020-12-13 tex/ms.tex
much better loading screen for app
new tests
set randomizer seed for test, duh

% Title
\title{%
    \textbf{
        Interpretable Gaussian Processes for Stellar Variability
    }
}

@@

Another big advantage of GPs is their flexibility. GPs are often dubbed
a class of ``non-parametric'' models, given that nowhere in the specification
of the GP is there an explicit functional form for $\mathbf{f}$. Rather, a GP
is a stochastic
process whose draws can in principle take on \emph{any} functional form,
subject, however, to certain smoothness and correlation criteria
of tunable strictness
that are fully
encoded in the covariance $\pmb{\Sigma}$. Importantly, the covariance
$\pmb{\Sigma}$ of a GP is assembled via a continuous \emph{kernel function} $k(t_i, t_j)$
that specifies the covariance between points at times $t = t_i$ and $t = t_j$:
%
\begin{align}
    \Sigma_{i,j} = k(t_i, t_j)
    \quad.
\end{align}
%
In many applications, particularly when modeling stellar light curves,
it is customary to restrict the problem by
assuming that the process is \emph{stationary}, such that we may write
%
\begin{align}
    \Sigma_{i,j} & = k(t_i, t_j)
    \nonumber                                    \\
                 & = k(\left| t_i - t_j \right|)
    \nonumber                                    \\
                 & \equiv k(\Delta t)
    \quad.
\end{align}
%
A stationary process is one that is independent of phase (or, in this case,
the actual value of the time $t$); rather, it depends only on the \emph{difference}
between the phases of two data points. The kernel of a stationary process is
therefore a one-dimensional function, typically chosen from a set of
standard functions with desirable smoothness and spectral properties.
Among a vast number of kernels are a few that are commonly used
in modeling stellar variability: the squared exponential kernel,
%
\begin{align}
    k_\mathrm{E^2}(\Delta t) = \sigma^2 e^{-\frac{\Delta t}{2\tau}}
    \quad,
\end{align}
%
the Mat\'ern-3/2 kernel,
%
\begin{align}
    k_\mathrm{M^\frac{3}{2}}(\Delta t) = \sigma^2 \left( 1 + \frac{\sqrt{3}\Delta t}{\tau} \right) e^{-\frac{\sqrt{3}\Delta t}{\tau}}
    \quad,
\end{align}
%
the exponential sine squared kernel,
%
\begin{align}
    k_\mathrm{S^2}(\Delta t) = \sigma^2 e^{-\Gamma\sin^2\left( \frac{\pi \Delta t}{P} \right)}
    \quad,
\end{align}
%
the cosine kernel,
%
\begin{align}
    k_\mathrm{C}(\Delta t) = \sigma^2 \cos\left( \frac{2\pi \Delta t}{P} \right)
    \quad,
\end{align}
%
or any linear combination and/or product of these. In the expressions above,
$\sigma$, $\tau$, $\Gamma$, and $P$ are
the \emph{hyperparameters} of the kernels.
Specifically, $\sigma^2$ is the variance (the value
of the kernel when $t_i = t_j$), $\tau$ is a typical timescale over which
data are correlated, $\Gamma$ is a dimensionless scale parameter, and $P$ is
a period. Once a kernel has been chosen, these scalar quantities fully
specify the covariance of the Gaussian process. GP-based inference
entails optimizing or sampling over these few quantities, which in many
cases can be done easily and efficiently.

@@

Our goal now is to expand the function above in spherical harmonics. To that end,
we note that in a frame where the spot is centered on $\hat{\mathbf{z}}$
(i.e., at polar angle $\vartheta = 0$), the brightness profile is azimuthally
symmetric, so the only nonzero coefficients in the spherical harmonic
expansion are those with order $m = 0$. The corresponding spherical harmonics are
simply proportional to the Legendre polynomials in $\cos\vartheta$, so our task is
simplified to finding the Legendre polynomial expansion of $b$.
Define a vector $\pmb{\vartheta}$ of $K$ equally-spaced points
between $0$ and $\pi$, with coefficients given by
%
\begin{align}
    \vartheta_k = \frac{k\pi}{K-1}
    \quad.
\end{align}
%
We wish to model the brightness evaluated at each $\vartheta_k$
as a weighted combination of Legendre polynomials,
%
\begin{align}
    \mathbf{B} \, \tilde{\mathbf{s}}(\rho) = \mathbf{b}(\rho)
\end{align}
%
%
where $\mathbf{b}(\rho)$ is computed by evaluating Equation~(\ref{eq:brvartheta})
at each of the $\vartheta_k$,
$\mathbf{B}$ is a design matrix whose columns are
the weighted Legendre polynomials,
%
\begin{align}
    B_{k,l} & = \sqrt{2l + 1} \, P_l\left( \cos \vartheta_k \right)
    \quad,
\end{align}
%
and $\tilde{\mathbf{s}}(\rho)$ are the coefficients of the expansion.
These are related to the full vector of spherical harmonic coefficients describing
the spot, $\mathbf{s}(\rho)$, by
%
\begin{align}
    s^l_m(\rho) = \tilde{s}_l(\rho) \delta_{m,0}
    \quad,
\end{align}
%
where $\delta$ is the Kronecker delta function.
To find the coefficients $\tilde{\mathbf{s}}(\rho)$, we solve the (linear) inverse problem,
%
\begin{align}
    \tilde{\mathbf{s}}(\rho) & = \mathbf{B}^+ \, \mathbf{b}(\rho)
\end{align}
%
%
where
%
\begin{align}
    \mathbf{B}^+ & = \mathbf{S} \Big(\mathbf{B}^\top \mathbf{B} +
    \epsilon \mathbf{I}\Big)^{-1} \mathbf{B}^\top
\end{align}
%
is the smoothed pseudo-inverse of $\mathbf{B}$ with small regularization
parameter $\epsilon$, $\mathbf{I}$ is the identity matrix, and
$\mathbf{S}$ is a diagonal smoothing matrix with coefficients
%
\begin{align}
    S_{k,l} = \exp\left[-\frac{l(l + 1)}{2\sigma^2}\right] \delta_{k,l}
\end{align}
%
for smoothing strength $\sigma$. For $\epsilon \rightarrow 0$ and
$\sigma \rightarrow \infty$,
$\mathbf{B}^+$ is the exact pseudo-inverse of
$\mathbf{B}$. However,
$\epsilon > 0$ is chosen for improved numerical stability and
$\sigma > 0$ is chosen to mitigate the effect of ringing in the solution.
In practice, we obtain good results with $\epsilon \approx 10^{-9}$
and $\sigma \approx 15$.

@@

\subsubsection{First moment}
%
The first moment of the radius distribution is (Equation~\ref{eq:e1})
%
\begin{align}
    \mathbf{e}_\rho
     & \equiv
    \int
    \mathbf{s}(\rho) \,
    p(\rho \, \big| \, \pmb{\theta}_{\rho}) \,
    \mathrm{d}\rho
    \nonumber \\
     & =
    \frac{1}{2\Delta}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    \mathbf{s}(\rho) \,
    \mathrm{d}\rho
    \quad.
\end{align}
%
Using the equations from the previous section, its components may be written
%
\begin{align}
    (e_\rho)^l_m
     & =
    \frac{\delta_{m,0}}{2\Delta}
    \int_{r - \Delta}^{r+ \Delta}
    \tilde{s}_{l}(\rho) \,
    \mathrm{d}\rho
    \nonumber \\
     & =
    \frac{\delta_{m,0}}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \int_{r - \Delta}^{r + \Delta}
    b_{k}(\rho)
    \mathrm{d}\rho
    \nonumber \\
     & =
    \frac{\delta_{m,0} s}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \ln
    \left(
    \frac{
        1+\exp\left(\frac{r -\Delta -\vartheta_k}{s}\right)
    }
    {
        1+\exp\left(\frac{r + \Delta -\vartheta_k}{s}\right)
    }
    \right)
    \quad.
\end{align}
%
In the limit $\Delta \rightarrow 0$,
%
\begin{align}
    \lim_{\Delta \rightarrow 0}
    \mathbf{e}_\rho
     & =
    \mathbf{B}^+ \mathbf{b}(r)
    \quad.
\end{align}
%

\subsubsection{Second moment}
%
The second moment of the radius distribution is (Equation~\ref{eq:E1})
%
\begin{align}
    \mathbf{E}_\rho
     & \equiv
    \int
    \mathbf{s}(\rho) \,
    \mathbf{s}^\top(\rho) \,
    p(\rho \, \big| \, \pmb{\theta}_{\rho}) \,
    \mathrm{d}\rho
    \nonumber \\
     & =
    \frac{1}{2\Delta}
    \int_{r - \Delta}^{r + \Delta}
    \mathbf{s}(\rho) \,
    \mathbf{s}^\top(\rho) \,
    \mathrm{d}\rho
    \quad.
\end{align}
%
As before, its components may be written
%
%
\begin{align}
    (E_\rho)^{l,l'}_{m,m'}
     & =
    \frac{\delta_{m,0}\delta_{m',0}}{2\Delta}
    \int_{r - \Delta}^{r + \Delta}
    \tilde{s}^l_{m}(\rho) \,
    \tilde{s}^{l'}_{m'}(\rho) \,
    \mathrm{d}\rho
    \nonumber \\
     & =
    \frac{\delta_{m,0}\delta_{m',0}}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \sum_{k'=0}^{K-1} B^+_{l',k'}
    \int_{r - \Delta}^{r + \Delta}
    b_{k}(\rho)
    b_{k'}(\rho)
    \mathrm{d}\rho
    \nonumber \\
     & =
    \frac{\delta_{m,0}\delta_{m',0}s}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \sum_{k'=0}^{K-1} B^+_{l',k'}
    C_{k,k'}(r,\Delta)
    \quad,
\end{align}
%
where
%
\begin{align}
    C_{k,k'}(r,\Delta)
     & \equiv
    \frac{
        \exp\left(\frac{\vartheta_{k} - \vartheta_{k'}}{s}\right)
        \ln
        \left(
        \frac{
            1+\exp\left(\frac{r -\Delta -\vartheta_{k}}{s}\right)
        }
        {
            1+\exp\left(\frac{r + \Delta -\vartheta_{k}}{s}\right)
        }
        \right)
        -
        \ln
        \left(
        \frac{
            1+\exp\left(\frac{r -\Delta -\vartheta_{k'}}{s}\right)
        }
        {
            1+\exp\left(\frac{r + \Delta -\vartheta_{k'}}{s}\right)
        }
        \right)
    }{
        1
        -
        \exp\left(\frac{\vartheta_{k} - \vartheta_{k'}}{s}\right)
    }
    \quad.
\end{align}
%
In the limit $\Delta \rightarrow 0$,
%
\begin{align}
    \lim_{\Delta \rightarrow 0}
    \mathbf{E}_\rho
     & =
    \mathbf{B}^+ \mathbf{b}(r) \mathbf{b}^\top(r) {\mathbf{B}^+}^\top
    \quad.
\end{align}
%

@@

@@

as the expectation of $\mathbf{y}$ in the polar frame at time $t = t_k$.

>>>>

% Title
\title{%
    \textbf{
        Interpretable Gaussian Processes for Stellar Variability\\
        I: Static Surfaces
    }
}

@@

Another big advantage of GPs is their flexibility. GPs are often dubbed
a class of ``non-parametric'' models, given that nowhere in the specification
of the GP is there an explicit functional form for $\mathbf{f}$. Rather, a GP
is a stochastic
process whose draws can in principle take on \emph{any} functional form,
subject, however, to certain smoothness and correlation criteria
of tunable strictness
that are fully
encoded in the covariance $\pmb{\Sigma}$. Importantly, the covariance
$\pmb{\Sigma}$ of a GP is assembled via a continuous \emph{kernel function} $k(t_i, t_j)$
that specifies the covariance between points at times $t = t_i$ and $t = t_j$:
%
\begin{align}
    \Sigma_{i,j} = k(t_i, t_j)
    \quad.
\end{align}
%
In many applications, particularly when modeling stellar light curves,
it is customary to restrict the problem by
assuming that the process is \emph{stationary}, such that we may write
%
\begin{align}
    \Sigma_{i,j} & = k(t_i, t_j)
    \nonumber                                    \\
                 & = k(\left| t_i - t_j \right|)
    \nonumber                                    \\
                 & \equiv k(\Delta t)
    \quad.
\end{align}
%
A stationary process is one that is independent of phase (or, in this case,
the actual value of the time $t$); rather, it depends only on the \emph{difference}
between the phases of two data points. The kernel of a stationary process is
therefore a one-dimensional function, typically chosen from a set of
standard functions with desirable smoothness and spectral properties.
Among a vast number of kernels are a few that are commonly used
in modeling stellar variability: the squared exponential kernel,
%
\begin{align}
    k_\mathrm{E^2}(\Delta t) = \sigma^2 \exp\left(-\frac{\Delta t}{2\tau}\right)
    \quad,
\end{align}
%
the Mat\'ern-3/2 kernel,
%
\begin{align}
    k_\mathrm{M^\frac{3}{2}}(\Delta t) = \sigma^2 \left( 1 + \frac{\sqrt{3}\Delta t}{\tau} \right) \exp\left(-\frac{\sqrt{3}\Delta t}{\tau}\right)
    \quad,
\end{align}
%
the exponential sine squared kernel,
%
\begin{align}
    k_\mathrm{S^2}(\Delta t) = \sigma^2 \exp\left[-\Gamma\sin^2\left( \frac{\pi \Delta t}{P} \right)\right]
    \quad,
\end{align}
%
the cosine kernel,
%
\begin{align}
    k_\mathrm{C}(\Delta t) = \sigma^2 \cos\left( \frac{2\pi \Delta t}{P} \right)
    \quad,
\end{align}
%
or any linear combination and/or product of these. In the expressions above,
$\sigma$, $\tau$, $\Gamma$, and $P$ are
the \emph{hyperparameters} of the kernels.
Specifically, $\sigma^2$ is the variance (the value
of the kernel when $t_i = t_j$), $\tau$ is a typical timescale over which
data are correlated, $\Gamma$ is a dimensionless scale parameter, and $P$ is
a period. Once a kernel has been chosen, these scalar quantities fully
specify the covariance of the Gaussian process. GP-based inference
entails optimizing or sampling over these few quantities, which in many
cases can be done easily and efficiently.

@@

Our goal now is to expand the function above in spherical harmonics. To that end,
we note that in a frame where the spot is centered on $\hat{\mathbf{z}}$
(i.e., at polar angle $\vartheta = 0$), the brightness profile is azimuthally
symmetric, so the only nonzero coefficients in the spherical harmonic
expansion are those with order $m = 0$. The corresponding spherical harmonics are
simply proportional to the Legendre polynomials in $\cos\vartheta$, so our task is
simplified to finding the Legendre polynomial expansion of $b$.
Define a vector $\pmb{\vartheta}$ of $K$ equally-spaced points
between $0$ and $\pi$, with coefficients given by
%
\begin{align}
    \vartheta_k = \frac{k\pi}{K-1}
    \quad.
\end{align}
%
We wish to model the brightness evaluated at each $\vartheta_k$
as a weighted combination of Legendre polynomials,
%
\begin{align}
    \mathbf{B} \, \tilde{\mathbf{s}}(\rho) = \mathbf{b}(\rho)
\end{align}
%
%
where $\mathbf{b}(\rho)$ is computed by evaluating Equation~(\ref{eq:brvartheta})
at each of the $\vartheta_k$,
$\mathbf{B}$ is a design matrix whose columns are
the weighted Legendre polynomials,
%
\begin{align}
    B_{k,l} & = \sqrt{2l + 1} \, P_l\left( \cos \vartheta_k \right)
    \quad,
\end{align}
%
and $\tilde{\mathbf{s}}(\rho)$ are the coefficients of the expansion.
These are related to the full vector of spherical harmonic coefficients describing
the spot, $\mathbf{s}(\rho)$, by
%
\begin{align}
    s^l_m(\rho) = \tilde{s}_l(\rho) \delta_{m,0}
    \quad,
\end{align}
%
or, in vector form,
%
\begin{align}
    \mathbf{s}(\rho) = \pmb{\mathcal{I}} \, \tilde{\mathbf{s}}(\rho)
\end{align}
%
where $\pmb{\mathcal{I}}$ is a rectangular
$\left( \left(l_\mathrm{max} + 1\right)^2 \times \left(l_\mathrm{max} + 1\right) \right)$
identity-like matrix with components
%
\begin{align}
    \mathcal{I}_{n, l} = \delta_{n, l^2 + l}
    \quad,
\end{align}
%
and $\delta$ is the Kronecker delta function.
To find the coefficients $\tilde{\mathbf{s}}(\rho)$
(and hence $\mathbf{s}(\rho)$), we solve the (linear) inverse problem,
%
\begin{align}
    \tilde{\mathbf{s}}(\rho) & = \mathbf{B}^+ \, \mathbf{b}(\rho)
\end{align}
%
%
where
%
\begin{align}
    \mathbf{B}^+ & = \mathbf{S} \Big(\mathbf{B}^\top \mathbf{B} +
    \epsilon \mathbf{I}\Big)^{-1} \mathbf{B}^\top
\end{align}
%
is the smoothed pseudo-inverse of $\mathbf{B}$ with small regularization
parameter $\epsilon$, $\mathbf{I}$ is the identity matrix, and
$\mathbf{S}$ is a diagonal smoothing matrix with coefficients
%
\begin{align}
    S_{k,l} = \exp\left[-\frac{l(l + 1)}{2\sigma^2}\right] \delta_{k,l}
\end{align}
%
for smoothing strength $\sigma$. For $\epsilon \rightarrow 0$ and
$\sigma \rightarrow \infty$,
$\mathbf{B}^+$ is the exact pseudo-inverse of
$\mathbf{B}$. However,
$\epsilon > 0$ is chosen for improved numerical stability and
$\sigma > 0$ is chosen to mitigate the effect of ringing in the solution.
In practice, we obtain good results with $\epsilon \approx 10^{-9}$
and $\sigma \approx 15$.

@@

\subsubsection{First moment}
%
The first moment of the radius distribution is (Equation~\ref{eq:e1})
%
\begin{align}
    \mathbf{e}_\rho
     & \equiv
    \int
    \mathbf{s}(\rho) \,
    p(\rho \, \big| \, \pmb{\theta}_{\rho}) \,
    \mathrm{d}\rho
    \nonumber \\
     & =
    \frac{1}{2\Delta}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    \mathbf{s}(\rho) \,
    \mathrm{d}\rho
    \quad.
\end{align}
%
Using the equations from the previous section, its components may be written
%
\begin{proof}{test_erho}
    (e_\rho)^l_m
    & =
    \frac{\delta_{m,0}}{2\Delta}
    \int_{r - \Delta}^{r+ \Delta}
    \tilde{s}_{l}(\rho) \,
    \mathrm{d}\rho
    \nonumber \\
    & =
    \frac{\delta_{m,0}}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \int_{r - \Delta}^{r + \Delta}
    b_{k}(\rho)
    \mathrm{d}\rho
    \nonumber \\
    & =
    \delta_{m,0}
    \sum_{k=0}^{K-1} B^+_{l,k}
    c_k(r, \Delta)
\end{proof}
%
where
%
\begin{proof}{test_erho}
    c_k(r, \Delta) & =
    \frac{s}{2\Delta}
    \ln
    \left(
    \frac{
            1+\chi_k^-(r, \Delta)
        }
        {
            1+\chi_k^+(r, \Delta)
        }
    \right)
\end{proof}
%
and
\begin{proof}{test_erho}
    \chi_k^-(r, \Delta) & \equiv \exp\left(\frac{r -\Delta -\vartheta_k}{s}\right)
    \nonumber                                                              \\
    \chi_k^+(r, \Delta) & \equiv \exp\left(\frac{r +\Delta -\vartheta_k}{s}\right)
    \quad.
\end{proof}
%
In vector form, we may simply write
%
\begin{proof}{test_erho}
    \mathbf{e}_\rho
    & =
    \pmb{\mathcal{I}} \,
    \mathbf{B}^+ \, \mathbf{c}(r, \Delta)
    \quad.
\end{proof}
%
Note, finally, that in the limit $\Delta \rightarrow 0$,
%
\begin{proof}{test_erho}
    \lim_{\Delta \rightarrow 0}
    \mathbf{e}_\rho
    & =
    \pmb{\mathcal{I}} \,
    \mathbf{B}^+ \mathbf{b}(r)
    \quad.
\end{proof}
%

\subsubsection{Second moment}
%
The second moment of the radius distribution is (Equation~\ref{eq:E1})
%
\begin{align}
    \mathbf{E}_\rho
     & \equiv
    \int
    \mathbf{s}(\rho) \,
    \mathbf{s}^\top(\rho) \,
    p(\rho \, \big| \, \pmb{\theta}_{\rho}) \,
    \mathrm{d}\rho
    \nonumber \\
     & =
    \frac{1}{2\Delta}
    \int_{r - \Delta}^{r + \Delta}
    \mathbf{s}(\rho) \,
    \mathbf{s}^\top(\rho) \,
    \mathrm{d}\rho
    \quad.
\end{align}
%
As before, its components may be written
%
%
\begin{proof}{test_bigErho}
    (E_\rho)^{l,l'}_{m,m'}
    & =
    \frac{\delta_{m,0}\delta_{m',0}}{2\Delta}
    \int_{r - \Delta}^{r + \Delta}
    \tilde{s}^l_{m}(\rho) \,
    \tilde{s}^{l'}_{m'}(\rho) \,
    \mathrm{d}\rho
    \nonumber \\
    & =
    \frac{\delta_{m,0}\delta_{m',0}}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \sum_{k'=0}^{K-1} B^+_{l',k'}
    \int_{r - \Delta}^{r + \Delta}
    b_{k}(\rho)
    b_{k'}(\rho)
    \mathrm{d}\rho
    \nonumber \\
    & =
    \delta_{m,0}\delta_{m',0}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \sum_{k'=0}^{K-1} B^+_{l',k'}
    C_{k,k'}(r,\Delta)
    \quad,
\end{proof}
%
where
%
\begin{proof}{test_bigErho}
    C_{k,k'}(r,\Delta)
    & \equiv
    \frac{s}{2\Delta}
    \begin{cases}
        \displaystyle
        \frac{
            \exp\left(\frac{\vartheta_{k} - \vartheta_{k'}}{s}\right)
            \ln
            \left(
            \frac{
                1+\chi_k^-
            }
            {
                1+\chi_k^+
            }
            \right)
            -
            \ln
            \left(
            \frac{
                1+\chi_{k'}^-
            }
            {
                1+\chi_{k'}^+
            }
            \right)
        }{
            1
            -
            \exp\left(\frac{\vartheta_{k} - \vartheta_{k'}}{s}\right)
        }
         & k \ne k'
        \\[0.5em]
        \frac{1}{1 + \chi_k^+}
        +
        \frac{\chi_k^-}{1 + \chi_k^-}
        -
        \ln\left( \frac{
            1 + \chi_k^-
        }{
            1 + \chi_k^+
        } \right)
        - 1
         & k = k'
        \quad.
    \end{cases}
\end{proof}
%
In vector form, this may be written
%
\begin{proof}{test_bigErho}
    \mathbf{E}_\rho
    &=
    \pmb{\mathcal{I}} \,
    \mathbf{B}^+ \mathbf{C} (r, \Delta) {\mathbf{B}^+}^\top
    \pmb{\mathcal{I}}^\top
    \quad.
\end{proof}
%
Finally, in the limit $\Delta \rightarrow 0$,
%
\begin{proof}{test_bigErho}
    \lim_{\Delta \rightarrow 0}
    \mathbf{E}_\rho
    & =
    \pmb{\mathcal{I}} \,
    \mathbf{B}^+ \mathbf{b}(r) \mathbf{b}^\top(r) {\mathbf{B}^+}^\top
    \pmb{\mathcal{I}}^\top
    \quad.
\end{proof}
%

@@

    \label{eq:eIk}

@@

as the expectation of $\mathbf{y}$ in the polar frame at time $t = t_k$.%
\footnote{In the presence of limb darkening, we must include the limb
    darkening operator $\mathbf{L}(\mathbf{u})$ in Equation~(\ref{eq:eIk});
    see \S\ref{sec:ld}.}
